%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}
% NOTE TO SELF I have many presentations where I was a secondary author. Need to decide how to include these.
% there's also a poster I presented at CQIQC...
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\cvsubsection{Contributed Talks and Posters}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{K. G. S. Xie}, C. J. Dale, K. Pond Grehan, M. F. Wang, Z. Yu, P. S. Julienne, T. Enss, and J. H. Thywissen. Clock shift and contact of a unitary Fermi gas inferred by dimer association. Oral presentation: DAMOP 2025, Portland, Oregon, U.S.A.}

   \cvpub{\textbf{K. G. S. Xie}, C. J. Dale, K. Pond Grehan, M. F. Wang, Z. Yu, P. S. Julienne, T. Enss, and J. H. Thywissen. In search of C: the need for speed. Oral presentation: TUCAN 2025, Waterloo, Ontario, Canada.}

    \cvpub{\textbf{K. G. S. Xie}, K. G. Jackson, C. J. Dale, K. Pond Grehan, J. Maki, D. J. M. Ahmed-Braun, S. Zhang, and J. H. Thywissen. Emergent \textit{s}-wave dimers near a \textit{p}-wave Feshbach resonance in a strongly confined Fermi gas. Oral presentation and poster: ICPEAC 2023, Ottawa, Ontario, Canada.}

    \cvpub{\textbf{K. G. S. Xie}, K. G. Jackson, C. J. Dale, K. Pond Grehan, J. Maki, S. Zhang, and J. H. Thywissen. Associating emergent \textit{s}-wave dimers along strongly confined directions of a spin-polarized Fermi gas. Oral presentation: DAMOP 2023, Spokane, Washington, U.S.A.}

    \cvpub{\textbf{K. G. S. Xie}, K. G. Jackson, C. J. Dale, J. Maki, B. A. Olsen, D. J. M. Ahmed-Braun, S. Zhang, and J. H. Thywissen. Emergent \textit{s}-wave interactions between identical fermions in quasi-one-dimensional geometries. Oral presentation: ICAP 2022, Toronto, Ontario, Canada.}

    \cvpub{\textbf{K. G. S. Xie}, K. G. Jackson, C. J. Dale, B. A. Olsen, J. Maki, S. Zhang, and J. H. Thywissen. Odd- and even-wave interactions between identical fermions in strong confinement. Poster: CQIQC IX, 2022, Toronto, Ontario, Canada.}

    \cvpub{\textbf{K. G. S. Xie}, K. G. Jackson, C. J. Dale, J. Maki, B. A. Olsen, D. J. M. Ahmed-Braun, S. Zhang, and J. H. Thywissen. Feshbach-enhanced odd- and even-wave interactions between identical fermions in quasi-one-dimensional confinement. Poster: ICAP 2022, Toronto, Ontario, Canada.}

    \cvpub{\textbf{K. G. S. Xie}, K. G. Jackson, C. J. Dale, J. Maki, B. A. Olsen, D. J. M. Ahmed-Braun, S. Kokkelmans, S. Smale, P. S. Julienne, and J. H. Thywissen. \textit{P}-wave interactions in a spin-polarized Fermi gas with and without confinement. Poster: DAMOP 2022, Orlando, Florida, U.S.A.}
\end{cvpubs}
